---
title: "Midterm in Class"
author: "Claire Dudley"
date: "3/9/2022"
output: html_document
---

“All work presented is my own. I have not communicated with or worked with anyone else on this exam.”
Claire Dudley

# Question 1 (20 points). Examine the following plot that uses the pokemon_full.csv data set. The plot gives the count of each Pokemon type.
```{r}
library(tidyverse)
library(here)
pokemon_df <- read_csv(here("data/pokemon_full.csv"))
pokemon_type <- pokemon_df %>% group_by(Type) %>% summarise(type_count = n())

ggplot(data = pokemon_type, aes(x = Type, y = type_count)) +
  geom_bar(stat = "identity") +
  labs(x = "Type",
       y = "Count") +
  coord_flip()
```

part a. Which of the 7 grammar of graphics parameters are explicitly specified in the code to make the plot?

  Data (pokemon_type), Mappings (aesthetics), Geom_function (geom_bar), Stat (identity), and Coordinate (coord_flip)
  
part b. For these types of plots, we have usually reordered the Type so that the type with the most Pokemon would be first and the type with the least number of pokemon would be last. Use a principle from the Data Visualization Reading to explain why we would want to do this.
  
  In Data Visualization Chapter 1, Look at data, they emphasize the importance of being able to distinguish between values' sizes in a chart. When the bars are all arranged in order of size, we can tell exactly which bars are larger than others and how close they are to each other.
  
part c. We have also stated that, for bar plots and lollipop plots, 0 should be included in the plot. On the other hand, for point plots and scatterplots, 0 need not be included. Using a principle from the Data Visualization Reading, explain why it is okay to omit 0 from a point plot but not from a bar plot.

  In Data Visualization Chapter 1, in section 1.6 Problems of honesty and good judgment they compare a bar plot that's scale goes to zero with a dot being confined to the range of values in the observation. They say a general rule of thumb is that bar charts should include a zero baseline as they encode their variables as lengths. Neither is really to be preferred, as both have their advantages - bar plots are less misleading in a way because they all scale back to 0, while it can be nice to show data just over the observed range, and sometimes more informative. 

# Question 2 (5 points). These points will be given for properly committing and pushing a .Rmd and a .html file with your exam answers.

# Question 3 (5 points). Tell me something you learned about ethics in data visualization.

  One thing I learned about ethics in data visualization is that if excluding data, you need both a good reason and to communicate you are doing so and why. This is to ensure you are being honest and not misleading when presenting data.

# Question 4 (20 points).

part a. A data set on United States election results was obtained from https://github.com/kjhealy/us_elections_2020_csv. Use the maps package, as well as this data set (posted on Sakai), to construct a map that fills each U.S. State with the percent of voters who voted for the republican candidate, Trump (percent_gop). 

```{r}
library(maps)
library(tidyverse)
library(here)
election_df <- read_csv(here("data/2020_county_pres.csv")) %>%
  group_by(state_name) %>%
  summarise(total_gop = sum(votes_gop),
            total_dem = sum(votes_dem)) %>%
  mutate(percent_gop = 100 * total_gop / (total_gop + total_dem)) %>%
  mutate(state_name = str_to_lower(state_name))

state_df <- ggplot2::map_data("state")

elect_full <- left_join(state_df, election_df, by = c("region" = "state_name"))
```

```{r}
ggplot(data = elect_full, aes(x = long, y = lat, group = group)) +
  geom_polygon(colour = "black", aes(fill = percent_gop)) +
  coord_map(projection = "albers", lat0 = 39, lat1 = 45) +
  theme_void() +
  scale_fill_distiller(direction = 1) +
  labs(fill = "Percent GOP")
```

part b. Explain why the data frame R needs to construct a map of the United States is much, much longer than 50 rows.

  To create a map of the United States, R needs individual longitude and latitude points for all of the borders of all of the country, which means a lot more than 50 rows.

# Question 5 (25 points). Construct a shiny app using the alcohol.csv data set that has a scatterplot of the number of wine servings vs. the number of beer servings. In the app, the user should be able to select a country and have a label for that country appear on the app.

In addition, create an input that lets the user choose a variable (either beer_servings, spirit_servings, and wine_servings) and create an output that is a histogram based on that variable.

```{r}
library(shiny)
library(ggrepel)
alcohol_df <- read_csv(here("data/alcohol.csv"))

var_choices <- names(alcohol_df)[c(2:4)]

ui <- fluidPage(
  sidebarLayout(
    sidebarPanel(selectInput("countrychoice", 
                             label = "Choose a Country",
                             choices = levels(factor(alcohol_df$country))),
                 radioButtons(inputId = "varselect",
                              label = "Choose a Variable",
                              choices = var_choices)),
    
    mainPanel(plotOutput("histplot"),
              plotOutput("scatterplot"))
  )
  
)

server <- function(input, output, session) {
  
  onecountry_df <-
    reactive({
      alcohol_df %>% dplyr::filter(country == input$countrychoice)})
  

  
  output$histplot <- renderPlot({
    ggplot(data = alcohol_df, aes(x = .data[[input$varselect]])) +
      geom_histogram(colour = "black", fill = "white", bins = 15)
  })
  
  output$scatterplot <- renderPlot({
    ggplot(data = alcohol_df, aes(x = beer_servings, y = wine_servings)) + 
      geom_point()  +
      geom_label_repel(data = onecountry_df(), aes(label = country))  +
      geom_point(data = onecountry_df(), size = 3, shape = 1)
  })
  
  
  
}

shinyApp(ui, server)
```

# Question 6 (10 points). For the following shiny app, draw a reactive graph. I think the easiest way to do this would be to hand-draw the graph and hand it in on a piece of paper (there is paper at the front of the room). If you can figure out a way to draw it on your computer, you may do that and push that file to GitHub.

# Question 7 (20 points). Consider again the women’s tennis data set, wta_matches_2019.csv, where each row corresponds to a match played on the WTA (Women’s Tennis Association) tour. 

```{r}
library(tidyverse)
library(here)
wta_df <- read_csv(here("data/wta_matches_2019.csv"))
```

```{r}
wta_long <- wta_df %>% pivot_longer(c(winner_name, loser_name),
                                    names_to = "won_or_lost",
                                    values_to = "player") %>%
  select(won_or_lost, player, everything())
```

```{r}
wta_better_players <-
  wta_long %>%
  group_by(player) %>%
  summarise(nmatch = n()) %>%
  filter(nmatch > 19)

wta_long2 <- left_join(wta_better_players, wta_long, by = "player")
```

```{r}
wta_long2$aces = ifelse(wta_long2$won_or_lost == "winner_name", wta_long2$w_ace, wta_long2$l_ace)
wta_long2 <- wta_long2[!is.na(wta_long2$aces),]
```

```{r}
wta_aces <-
  wta_long2 %>%
  group_by(player) %>%
  summarise(meanaces = mean(aces)) %>%
  mutate(player = fct_reorder(player, meanaces))
```

```{r}
ggplot(data = wta_aces, aes(x = player, y = meanaces)) + 
  geom_point() + 
  geom_segment(aes(x = player, xend = player, y = 0, yend = meanaces)) + 
  coord_flip() + 
  labs(y = "Mean Number of Aces",
       x = "Player") +
  theme(text = element_text(size = 6) ) 
```

# Question 8 (20 points).

part a. Consider the lollipop plot you made in Question 7. Why is this plot not the best plot to make to look at the top women’s servers in 2019? (There might be a couple of reasons but you should reference one that we have explicitly talked about in class a lot).
  
  This plot is not the best because all it shows us is the mean number of aces of a tennis player and shows us none of the variability. It would be better if it showed some kind of standard deviation or variability.

part b. Fix the plot so that it no longer has the issue you described in Question 8a. 

```{r}
wta_both <- left_join(wta_long2, wta_aces) %>%
  mutate(player = fct_reorder(player, meanaces))
ggplot(data = wta_both, aes(x = player, y = aces)) +
  geom_point(alpha = 0.2) +
  geom_point(data = wta_both, aes(y = meanaces, colour = "Mean Aces")) +
  coord_flip() +
  scale_colour_manual(values = c("Mean Aces" = "red")) +   labs(y = "Number of Aces",
       x = "Player") +
  theme(text = element_text(size = 6) ) 
```

