---
title: "Homework 2/14"
output: html_document
---
I worked with Kaden Pickering and Emil Zetterquist on this homework.
```{r}
library(tidyverse)
library(maps)
library(here)
hpi_df <- read_csv(here("data/hpi-tidy.csv"))
world_df <- ggplot2::map_data("world")
world_df %>% nrow()
```

## Exercise 1
```{r}
ggplot(data = world_df,
       mapping = aes(x = long, y = lat,
                     group = group)) + 
    geom_polygon(fill = "white", colour = "black") +
  coord_map(projection = "albers", lat0 = 39, lat1 = 45) +
  theme(axis.text = element_blank()) +
  theme_void() + 
  coord_map(projection = "mercator")
```

```{r}
world_df <-
  world_df %>%
  rename("Country" = "region")
```

```{r}
hpi_world <-
  left_join(world_df, hpi_df,
            by = "Country")
```

```{r}
ggplot(data = hpi_world,
       mapping = aes(x = long, y = lat,
                     group = group, fill = LifeExpectancy)) + 
    geom_polygon(colour = "black") +
  theme_void() + 
  coord_map(projection = "mercator") +
  scale_fill_viridis_c()
```

## Exercise 2
```{r}
world_df <-
  world_df %>%
  mutate(across("Country", str_replace, "USA", "United States of America"))
```

```{r}
hpi_world <-
  left_join(world_df, hpi_df,
            by = "Country")
```

```{r}
ggplot(data = hpi_world,
       mapping = aes(x = long, y = lat,
                     group = group, fill = LifeExpectancy)) + 
    geom_polygon(colour = "black") +
  theme_void() + 
  coord_map(projection = "mercator") +
  scale_fill_viridis_c()
```

## Exercise 3

```{r}
ggplot(data = hpi_world,
       mapping = aes(x = long, y = lat,
                     group = group, fill = LifeExpectancy)) + 
    geom_polygon(colour = "black") +
  theme_void() + 
  coord_map(projection = "mercator", xlim = c(-180,180)) +
  scale_fill_viridis_c()
```

## Exercise 4

  The Mercator projection makes countries closer to the poles distortedly big. Greenland is 550% too big in the Mercator projection as it appears the same size as Africa when it should fit into Africa 14 times.
  
## Exercise 5

```{r}
ggplot(data = hpi_world,
       mapping = aes(x = long, y = lat,
                     group = group, fill = LifeExpectancy)) + 
    geom_polygon(colour = "black") +
  theme_void() + 
  coord_map(projection = "globular", xlim = c(-180,180)) +
  scale_fill_viridis_c()
```

```{r}
ggplot(data = hpi_world,
       mapping = aes(x = long, y = lat,
                     group = group, fill = LifeExpectancy)) + 
    geom_polygon(colour = "black") +
  theme_void() + 
  coord_map(projection = "gilbert", xlim = c(-180,180)) +
  scale_fill_viridis_c()
```

In both projections, Greenland becomes relatively much smaller than the mercator projection. Greenland is especially small in the globular projection.

