---
title: "Homework Feb 28"
output: html_document
---

Exercise 1. In the tennis app, change the histogram input from a sliderInput() to a numericInput().
```{r}
library(tidyverse)
```


```{r}

var_choices <- names(df)[3:7]

library(shiny)

ui <- fluidPage(
  sidebarLayout(sidebarPanel(
    selectizeInput("playerchoice",
                   label = "Choose a Player", choices = levels(factor(df$player)),
                   selected = "Aryna Sabalenka"),
    radioButtons("varchoice", label = "Choose a Statistic",
                 choices = var_choices),
    numericInput("binnumber", label = "Choose a Number of Bins", 
                min = 1, max = 50, value = 15, step = 1)),
    mainPanel(plotOutput("histgraph"))
  )
)

server <- function(input, output, session) {
  
  df_sub <- reactive({
    df %>% filter(player == input$playerchoice)
  })
  
  hist_plot <- reactive({
    # ggplot(df_sub(), aes_string(x = input$varchoice)) +
    # geom_histogram(colour = "black", fill = "white", bins = 15)
    ggplot(df_sub(), aes(x = .data[[input$varchoice]])) +
      geom_histogram(colour = "black", fill = "white", bins = input$binnumber) +
      theme_grey(base_size = 22)
  })
  
  output$histgraph <- renderPlot({
    hist_plot()
  })
  

}

shinyApp(ui, server)
```


Exercise 2. In the tennis app, change the histogram input back to sliderinput(). Then, apply 2.2.8 Exercise 3 in Mastering Shiny to the tennis app slider.

```{r}
var_choices <- names(df)[3:7]

library(shiny)

ui <- fluidPage(
  sidebarLayout(sidebarPanel(
    selectizeInput("playerchoice",
                   label = "Choose a Player", choices = levels(factor(df$player)),
                   selected = "Aryna Sabalenka"),
    radioButtons("varchoice", label = "Choose a Statistic",
                 choices = var_choices),
    sliderInput("binnumber", label = "Choose a Number of Bins", 
                min = 0, max = 100, value = 15, step = 5, animate = TRUE)),
    mainPanel(plotOutput("histgraph"))
  )
)

server <- function(input, output, session) {
  
  df_sub <- reactive({
    df %>% filter(player == input$playerchoice)
  })
  
  hist_plot <- reactive({
    # ggplot(df_sub(), aes_string(x = input$varchoice)) +
    # geom_histogram(colour = "black", fill = "white", bins = 15)
    ggplot(df_sub(), aes(x = .data[[input$varchoice]])) +
      geom_histogram(colour = "black", fill = "white", bins = input$binnumber) +
      theme_grey(base_size = 22)
  })
  
  output$histgraph <- renderPlot({
    hist_plot()
  })
  

}

shinyApp(ui, server)
```


Exercise 3. In the SLU majors app, change the major input to radioButtons() so that the user can only select mathematics, statistics, or computer science as the major.
```{r}
df <- read_excel(here("data/slu_graduates_17_21.xlsx"))

## fixes error in the data
df <- df %>% mutate(across(everything(),
                           .fns = ~replace(., . == "STATS" , "STAT")))

df_long <- df %>% pivot_longer(3:8, names_to = "type", values_to = "discipline")
df_major <- df_long %>%
  filter(type == "major1" | type == "major2" | type == "major3")

df_stat <- df_major %>% filter(discipline == "STAT")
df_statfull <- semi_join(df_long, df_stat, by = "adm_id") %>%
  filter(type == "major1" |
           type == "major2" |
           type == "major3")

df_nostat <- df_statfull %>% filter(discipline != "STAT" &
                                      !is.na(discipline)) %>%
  group_by(discipline) %>%
  summarise(nstudent = n()) %>%
  mutate(discipline = fct_reorder(discipline, nstudent))

df_math_maj <- df_statfull %>%
  filter(major)
```

```{r}
library(shiny)

ui <- fluidPage(
  sidebarLayout(
    sidebarPanel(radioButtons(inputId = "majorchoice",
                                label = "Choose a Major",
                                choices = list("CS", "STAT", "MATH"))),
    mainPanel(plotOutput(outputId = "majorplot"))
  )
)

server <- function(input, output, session) {
  
  df_update <- reactive({
    df_stat <- df_major %>% filter(discipline == input$majorchoice)
    
    
    df_statfull <- semi_join(df_long, df_stat, by = "adm_id") %>%
      filter(type == "major1" |
               type == "major2" |
               type == "major3")
    
    df_nostat <- df_statfull %>% filter(discipline != input$majorchoice &
                                          !is.na(discipline)) %>%
      group_by(discipline) %>%
      summarise(nstudent = n()) %>%
      mutate(discipline = fct_reorder(discipline, nstudent))
    
  })
  
  output$majorplot <- renderPlot({
    ggplot(data = df_update(), aes(x = discipline, y = nstudent)) +
      geom_col() +
      coord_flip()
  })
}

shinyApp(ui, server)

```


Exercise 4. In the SLU majors app, add a table output below the plot that shows the number of Female majors and the number of Male majors for a major that the user selects.

```{r}
library(shiny)

ui <- fluidPage(
  sidebarLayout(
    sidebarPanel(selectizeInput(inputId = "majorchoice",
                                label = "Choose a Major",
                                choices = factor(df$major1))),
    mainPanel(plotOutput(outputId = "majorplot"),
              tableOutput("table"))
  )
)

server <- function(input, output, session) {
  
  df_update <- reactive({
    df_stat <- df_major %>% filter(discipline == input$majorchoice)
    
    
    df_statfull <- semi_join(df_long, df_stat, by = "adm_id") %>%
      filter(type == "major1" |
               type == "major2" |
               type == "major3")
    
    df_nostat <- df_statfull %>% filter(discipline != input$majorchoice &
                                          !is.na(discipline)) %>%
      group_by(discipline) %>%
      summarise(nstudent = n()) %>%
      mutate(discipline = fct_reorder(discipline, nstudent))
    
  })
  # tried to use this to display sex in table, couldn't get it to work
# df_update2 <- reactive({
  #  df_stat <- df_major %>% filter(discipline == input$majorchoice)
    
    
  #  df_statfull <- semi_join(df_long, df_stat, by = "adm_id") %>%
  #    filter(type == "major1" |
  #             type == "major2" |
  #             type == "major3")
    
  #  df_nostat <- df_statfull %>% filter(discipline != input$majorchoice &
  #                                        !is.na(discipline)) %>%
   #   group_by(sex) %>%
   #   summarise(nstudent = n()) %>%
   #   ungroup() %>%
     # group_by(discipline) %>%
    #  mutate(discipline = fct_reorder(discipline, nstudent))
    
# })

  
  output$majorplot <- renderPlot({
    ggplot(data = df_update(), aes(x = discipline, y = nstudent)) +
      geom_col() +
      coord_flip()
  })
  
  output$table <- renderTable({
    df_update()
  })
}

shinyApp(ui, server)

```

