---
title: "homework_march7"
output: html_document
---

Given this UI:

ui <- fluidPage(
  textInput("name", "What's your name?"),
  textOutput("greeting")
)

Fix the simple errors found in each of the three server functions below. First try spotting the problem just by reading the code; then run the code to make sure you’ve fixed it.

server1 <- function(input, output, server) {
  input$greeting <- renderText(paste0("Hello ", name))
}

The problem with server 1 is that it says input$greeting instead of output$greeting:
```{r}
server1 <- function(input, output, server) {
  output$greeting <- renderText(paste0("Hello ", name))
}
```


server2 <- function(input, output, server) {
  greeting <- paste0("Hello ", input$name)
  output$greeting <- renderText(greeting)
}

In server 2, there are two lines where there should be one line. Should just be: 
```{r}
server2 <- function(input, output, server) {
  output$greeting <- paste0("Hello ", input$name)
}
```



server3 <- function(input, output, server) {
  output$greting <- paste0("Hello", input$name)
}

The problem with server 3 is that greeting is spelled wrong:
```{r}
server3 <- function(input, output, server) {
  output$greeting <- paste0("Hello", input$name)
}
```


2. Draw the reactive graph for the following server functions:


```{r}
erver1 <- function(input, output, session) {
  c <- reactive(input$a + input$b)
  e <- reactive(c() + input$d)
  output$f <- renderText(e())
}
server2 <- function(input, output, session) {
  x <- reactive(input$x1 + input$x2 + input$x3)
  y <- reactive(input$y1 + input$y2)
  output$z <- renderText(x() / y())
}
server3 <- function(input, output, session) {
  d <- reactive(c() ^ input$d)
  a <- reactive(input$a * 10)
  c <- reactive(b() / input$c) 
  b <- reactive(a() + input$b)
}
```



