---
title: "Quiz 4 In Class"
output: html_document
---

“All work presented is my own. I have not communicated with or worked with anyone else on this quiz.”
Claire Dudley

```{r}
library(tidyverse)
library(here)
alcohol_df <- read_csv(here("data/alcohol.csv"))
world_df <- ggplot2::map_data("world")
```

## Question 1
```{r}
world_df <-
  world_df %>%
  rename("country" = "region")
```

```{r}
alcohol_map <-
  left_join(world_df, alcohol_df,
            by = "country")
```

```{r}
ggplot(data = alcohol_map,
       mapping = aes(x = long, y = lat,
                     group = group, fill = beer_servings)) + 
    geom_polygon(colour = "black") +
  theme_void() + 
  coord_map(projection = "gilbert", xlim = c(-180,180)) +
  scale_fill_viridis_c()
```

## Question 2

If I were curious about looking at this dataset across time by adding a year variable, I would want to display the data in something other than a map, like a line chart across the years faceted by region. Looking at a map is just showing us the number of servings per person per year.

